---
title: "assign4"
author: "Ankie Fan"
date: "2022-10-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# assignment 4
## a) Distribution:
Binomial distribution, since the result of a play can only be a win or loss.  

## b)
Null hypothesis: the player is a fair player.  
Distribution: $X_f \sim Bin(100, \frac{1}{37})$  

## c) 
Alternative hypothesis: the player is a cheater.  
Distribution: $X_c \sim Bin(100, \frac{1}{20})$  

## d)
Confidence interval.

## e)
The decision rule should detect cheating players with a probability of 80%. This also means that there's 20% probability that this rule identifies cheaters as fair players. And this is Type 2 error.  
So we have 1 - P(type 2 error) = 0.8  
P(type 2 error) = 0.2  
We want to find a $c$ where:  
$P(accept \  H_0 | H_1) = P(X \leq c|p = \frac{1}{20}) = \sum^{0}_{i = c} P(X = i|p = \frac{1}{20})$  

```{r}

for(c in 1:100){
  s = pbinom(c,100,0.05)
  if (s <= 0.2){
    cat("c = ",c)
    cat("s = ",s)
  }
}
```
100 - 2 = 98  
So the rule is: if a player wins 98 or more than 98 times, we can say they have 80% possibility to be a cheater.  

## f)
Significance level

## g)
The possibility should be:  
```{r}
1 - pbinom(2,100,1/37)
```

## h)
Increasing the number of wins out of 100 which is used to determine cheating

## i)
$\alpha$ will increase (more fair players will be recognized as cheater)  
$\beta$ will decrease (less cheaters will be recognized as fair players)  