---
title: "Assign1"
author: "Ankie Fan"
date: "2022-09-16"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---
# Assignment 1
## Question 1
k people come to the theater  
Let X be the number of coming people  
$X\sim~ Bin(n,p)$, where n = 100, p = 0.5, k = 50, 51, 52... 100  
$P(X = k) = \begin{pmatrix} n \\ k \end{pmatrix} p^k(1-p)^{n-k}$  
$P(X > 50) = \sum^{100}_{k = 51}P(X = k) \approx 0.46$  
  
In python:
```
from scipy import stats
import numpy as np

p = stats.binom.pmf(np.arange(51,100,1),100,0.5)
p.sum()
```
In R:  
In R `pbinom` calculate $P(X \leq 50)$. So we use 1 to subtract it.  
```{r}
1-pbinom(50,100,0.5)
```
Or we can also think in this way:  
Since the possibility of a person will come is 50%, the possibility of no person comes and 100 people come should be the same. So we have:  
$P(X=0)=P(X=100),P(X=1)=P(X=99), ... ,P(X=49)=P(X=51)$ (a)  
So we have:  
$P(X=0) + P(X=1) + ... +P(X=100) = P(X=50)+2(P(X=51)+P(X=52)+...+P(X=100)) = P(X=50)+2P(X>50)$  
And:  
$P(X=50) = \begin{pmatrix} 100 \\ 50 \end{pmatrix} 0.5^{50}(1-0.5)^{50}$  
Since the total possibility of X = 0 to X = 100 should be 1,  
$P(X>50) = (1 - P(X=50))/2$  

Implementation in R:
```{r}
(1-dbinom(50,100,0.5))/2
```
This question is just like, there are 100 coins, what's the possibility that there are more than 50 coins are head.  

## Question 2
1. X is throwing a dice, Y is throwing a same dice. X and Y are independent and identically distributed.  
2. X is throwing a dice, Y is draw one card from the 52 cards. X and Y are independent and not identically distributed.  
3. In a group project, X is my grade, Y is my group mate's grade. X and Y are dependent and identically distributed.
4. X is drawing one card from the 52 cards, Y is drawing one card from 51 cards without the X one. X and Y are dependent and not identically distributed.